### 2019-05-14 README.Rmd
pseudoR2_not_S3method

<!-- badges: start -->
[![GPLv3 license](https://img.shields.io/badge/License-GPLv3-blue.svg)](https://www.r-project.org/Licenses/GPL-3)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/agrobioinfoservices/gosset?branch=master&svg=true)](https://ci.appveyor.com/project/kauedesousa/gosset)
<!-- badges: end -->

>>>>

<!-- badges: start -->
[![GPLv3 license](https://img.shields.io/badge/License-GPLv3-blue.svg)](https://www.r-project.org/Licenses/GPL-3)
[![CRAN status](https://www.r-pkg.org/badges/version/gosset){data-external="1"}](https://cran.r-project.org/package=gosset)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/agrobioinfoservices/gosset?branch=master&svg=true)](https://ci.appveyor.com/project/kauedesousa/gosset)
[![Build Status](https://travis-ci.org/agrobioinfoservices/gosset.svg?branch=master)](https://travis-ci.org/agrobioinfoservices/gosset)
[![codecov](https://codecov.io/gh/agrobioinfoservices/gosset/master.svg)](https://codecov.io/github/agrobioinfoservices/gosset?branch=master)
<!-- badges: end -->
